---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tppr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of tppr is to gather all the functions that are needed to recreate the results of the [Transparent Psi Project](https://osf.io/jk2zf/). The analysis can be run locally from R, but the package also includes a Shiny app, that allows people interested in the project to follow the results of the study real-time.

## Installation

You can install the development version (tppr is not available on CRAN) from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
# devtools::install_github("marton-balazs-kovacs/tppr")
```

## Using the app

The Shiny app is hosted on: ADD LINK

However, you can run the app locally.

```{r}
# tppr::run_app()
```

## Using the package

You can read more about how the functions included in the package work in `vignette("use_pkg")`.

Features coming soon:
* Reproducing the paper locally

## Code of Conduct
  
Please note that the tppr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
